---
title: Bar Plots, Bar None
author: Sophia Jensen
date: '2017-10-03'
slug: bar-plots-bar-none
categories:
  - ggplot2
  - R
tags:
  - data visualization
  - sql
  - bar plots
---

Welcome back to our final installment of ggplot2 data visualization! Today, we are doing bar plots!

```{r message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

A bar plot lays out the different levels of an attribute or factor! We will look at the team homerun totals for all the MLB teams in 1980.

```{r}
query<-"SELECT name,HR FROM Teams WHERE yearID=1980 ORDER BY HR "
result<-sqldf(query)

result$name<-factor(result$name,levels=result$name)
```

The last line is saving the information as a factor, and letting the system know that the order the results appear in the order we specified, not default alphabetical.

```{r}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity')+
  coord_flip()+
  ggtitle("1980 Team Homerun Totals")+
  xlab("Team Name")+
  ylab("Homeruns")
```

And there we have it! It is the same process as the other data visualizations that we have done through ggplot2. Differences are: saying geom_bar to specify bar plot format, saying stat='identity' to get the correct label, and using coord_flip to put the bars horizontal instead of vertical.

That's all folks! Thanks for hanging out!